---
title: "ClassWork5 Section 8.1"
author: "" #change to your group number
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



##Practice 1
(Example 8.1 continued): 
Let us use the same experiment and test statistic $X$ as previously described in the automobile bumper problem but now consider the rejection region $R_9 = \{9,10,...,20\}$. $X$ still has a binomial distribution with parameters $n = 20$ and $p = .25$.

TASK: Find type I ($\alpha$) and type II ($\beta$) errors.

DATA:
```{r}
n <- 20
p0 <- .25
```

##Part1
Type I error, $\alpha$, is calculated as follows, type the formul below:
\begin{align*}
\alpha =& P(\text{type I error}) = P(\text{$H_0$ is rejected when it is true})\\
=& P(X \ge 9 \;\text{when}\; X \sim Bin(20, .25)) = 1 - B(8; 20, .25)
\end{align*}


##Part 2
Calculate Type I error
```{r}
alpha <- 1 - pbinom(8, n, p0)
alpha
```

Type II errors, $\beta$, for $p=.3, p=.5$ are
\begin{align*}
\beta(.3) =& P(\text{type II error when $p = .3$})\\
=& P(\text{$H_0$ is not rejected when it is false because $p=.3$})\\
=& P(X \le 8 \; \text{when}\; X \sim Bin(20, .3)) = B(8; 20, .3)\\
\beta(.5) =& B(8; 20, .5)
\end{align*}

##Part 3
Calculut Type II error
```{r}
p_beta <- c(.3, .5) 
beta <- pbinom(8, n, p_beta)
beta

```

Read yourself: Here, the type I error probability has been decreased by using the new rejection region. However, a price has been paid for this decrease. $\beta$’s are larger than the corresponding error probabilities .772 and .132 for the region $R_8$. In retrospect, this is not surprising; $\alpha$ is computed by summing over probabilities of test statistic values in the rejection region, whereas $\beta$ is the probability that $X$ falls in the complement of the rejection region. Making the rejection region smaller must therefore decrease $\alpha$ while increasing $\beta$ for any $p > .25$.


##Practice 2

The drying time of a certain type of paint under specified test conditions is known to be normally distributed with mean value 75 min and standard deviation 9 min. Chemists have proposed a new additive designed to decrease average drying time. It is believed that drying times with this additive will remain normally distributed with $\sigma = 9$. Because of the expense associated with the additive, evidence should strongly suggest an improvement in average drying time before such a conclusion is adopted. Let $\mu$ denote the true average drying time when the additive is used. The appropriate hypotheses are 

$$H_0: \mu_0 = 75  \quad \text{versus} \quad H_a: \mu_A < 75 = \mu_0$$.

## Design the Hypothesis Test

Experimental data is to consist of drying times from $n = 25$ test specimens. Let $X_1, ..., X_{25}$ denote the 25 drying times—a random sample of size 25 from a normal distribution with mean value $\mu$ and standard deviation $\sigma = 9$. 

The sample mean dying time $\bar{X}$ then has a normal distribution with expected value $\mu_{\bar{X}} = \mu$ and standard deviation $\sigma_{\bar{X}} = \frac{\sigma}{\sqrt{n}} = \frac{9}{\sqrt{25}} = \frac{9}{5} = 1.80$. Thus  

$$
\bar{X} \; \thicksim \mathcal{N}\left(\mu,\sigma = \frac{9}{5}\right)
$$


When $H_0$ is true, $\mu_{\bar{X}} = 75$, so only an $\bar{x}$ value substantially less than 75 would strongly contradict $H_0$. 

These are the two competing hypotheses:
$$ 
\color{blue}{H_0:  \bar{X} \; \thicksim \mathcal{N}\left(\mu_0,\sigma = \frac{9}{5}\right),   \; \text{with} \; \mu_0 = 75}
\hspace{1in}
\color{red}{H_A: \bar{X} \; \thicksim \mathcal{N}\left(\mu_A,\sigma = \frac{9}{5}\right),   \; \text{with} \; \mu_A < \mu_0}
$$
\vspace{1.7in}


A reasonable rejection region has the form $\bar{x} \le c$, where the cutoff value $c$ is suitably chosen. 
Consider the choice $c = 70.8$.

The test procedure consists of test statistic $\bar{X}$ and rejection region $\bar{x} \le 70.8$. 

Because the rejection region consists only of small values of the test statistic, the test is said to be lower-tailed.

TASK: Find type I ($\alpha$) and type II ($\beta$) errors.

DATA:
```{r}
n <- 25
s <- 9
s_x <- s/sqrt(n)
mu <- 75
c <- 70.8
```

\textbf{Type I Error}, $\alpha$, is calculated as follows:

\begin{align*}
\alpha =& \text{type I error}  = \mathbf{P(R|H_0)} = P(\text{$H_0$ is rejected when it is true})\\
=& P\left(\text{$\bar{X}  \le 70.8$ when $\bar{X}  \sim \mathcal{N}\left(\mu_0=75,\sigma = \frac{9}{5}\right)$}\right)\\
=& \Phi \left( \frac{70.8 - 75}{1.8} \right) = pnorm\left(\frac{70.8 - 75}{1.8} \right) = pnorm\left(70.8, 75, 1.8\right)
\end{align*}

##Part 1
Compute Type I error
```{r}
alpha = pnorm(c,mu,1.8);alpha


```



\textbf{Type II Error} There is a different $\beta$ for each different $\mu_A$. For example, $\beta$ for $\mu_A=72$ is calculated as follows:

$$ 
\color{blue}{H_0:  \bar{X} \; \thicksim \mathcal{N}\left(\mu_0,\sigma = \frac{9}{5}\right),   \; \text{with} \; \mu_0 = 75}
\hspace{1in}
\color{red}{H_A: \bar{X} \; \thicksim \mathcal{N}\left(\mu_A,\sigma = \frac{9}{5}\right),   \; \text{with} \; \mathbf{\mu_A = 72}}
$$


\vspace{2in}

\begin{align*}
\beta(72) =& \left[\text{type II error when } \mu_A = 72 \right] = \mathbf{P(A|H_A)} =\\
=& P(\text{$H_0$ is not rejected when it is false because $\mu = 72$})\\
=& P\left(\text{$\bar{X} > 70.8$ when $\mathcal{N}\left(\mu_A=72,\sigma = \frac{9}{5}\right)$}\right)\\
=& \Phi \left( 1- \frac{70.8 - 72}{1.8} \right) = pnorm\left( 1- \frac{70.8 - 72}{1.8} \right) = 
pnorm\left( 70.8, 72,1.8, lower.tail = FALSE \right)
\end{align*}

##Part 2
Compute Type II error
```{r}

beta = pnorm(70.8, 72,1.8, lower.tail = FALSE);beta
```

For the specified test procedure, only 1% of all experiments carried out as described will result in $H_0$ being rejected when it is actually true. 

However, the chance of a type II error is very large when $\mu = 72$ (only a small departure from $H_0$), somewhat less when $\mu = 70$, and quite small when $\mu = 67$ (a very substantial departure from $H_0$). 

Notice that $\alpha$ is computed using the probability distribution of the test statistic when $H_0$ is true, whereas determination of $\beta$ requires knowing the test statistics distribution when $H_0$ is false.



## Run the test

You are given the $n=25$ tests specimens


67 67 68 66 71 67 68 71 71 67 70 71 69 69 70 67 68 71 66 67 71 70 69 66 65



To load the list in a vector x, we can use scan()
```{r}
# copy the list by selecting the 25 values
x <- scan() 
# now paste the 25 values, and hit return
```

```{r}
x <- c(67,67,68,66,71,67,68,71,71,67,70,71,69,69,70,67,68,71,66,67,71,70,69,66,65)
```




The test statistics is $\bar{X}$, since we are questioning the true value of $\mu$.

```{r}
xbar <- mean(x); xbar
```

### Result of the Hypotheses test

Recall that the rejection region is 
$$
\text{Rejection interval } = (0, 70.8) 
$$

The test depends on the answer to the following question:

\color{red}{Is $\bar{x}= 68.48$ in the Rejection interval?}

IF \textbf{YES}  then  \textbf{REJECT} THE NULL HYPOTHESIS

IF \textbf{NO} then \textbf{FAIL TO REJECT} THE NULL HYPOTHESIS


##Practice 3
(Practice 2 continued): 
The use of cutoff value $c = 70.8$ in the paint-drying example resulted in a very small value of $\alpha (.01)$ but rather large $\beta$’s. Consider the same experiment and test statistic $\bar{X}$ with the new rejection region $\bar{x} \le 72$. $\bar{X}$ is still normally distributed with mean value $\mu_{\bar{X}} = \mu$ and $\sigma_{\bar{X}} = 1.8$.

TASK: Find type I ($\alpha$) and type II ($\beta$) errors.

DATA:
```{r}
n <- 25
s <- 9
s_x <- s/sqrt(n)
mu <- 75
c <- 72
```

Type I error, $\alpha$, is calculated as follows:

\begin{align*}
\alpha =& \text{type I error}  = \mathbf{P(R|H_0)} = P(\text{$H_0$ is rejected when it is true})\\
=& P\left(\text{$\bar{X}  \le 72$ when $\bar{X}  \sim \mathcal{N}\left(\mu_0=75,\sigma = \frac{9}{5}\right)$}\right)\\
=& \Phi \left( \frac{72 - 75}{1.8} \right) = pnorm\left(\frac{72 - 75}{1.8} \right) = pnorm\left(72, 75, 1.8\right)
\end{align*}

##Part1 
Compute Type I error
```{r}
alpha = pnorm(c,mu,1.8);alpha
```




##Part 2 
Compute Type II error
Lets use 73 as an alternative mean. 
```{r}
beta = pnorm(c, 73,1.8, lower.tail = FALSE);beta

```

The change in cutoff value has made the rejection region larger (it includes more $\bar{x}$ values), resulting in a decrease in $\beta$ for each fixed $\mu$ less than 75. However, $\alpha$ for this new region has increased from the previous value .01 to approximately .05. If a type I error probability this large can be tolerated, though, the second region ($c = 72$) is preferable to the first($c = 70.8$) because of the smaller $\beta$’s.


