---
title: "PreWK3"
author: "Roy, Aniket" # change this line to have your name hear
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note: Please turn in both RMD file and pdf file to Canvas**


## PreWork 3


##Pratice 1

Natural cork in wine bottles is subject to deterioration, and as a result wine in such bottles may experience contamination. The article ``Effects of Bottle Closure Type on Consumer Perceptions of Wine Quality'' (Amer. J. of Enology and Viticulture, 2007: 182–191) reported that, in a tasting of commercial chardonnays, 16 of 91 bottles were considered spoiled to some extent by cork-associated characteristics.

TASK: Does this data provide strong evidence for concluding that more than 15% of all such bottles are contaminated in this way? Let’s carry out a test of hypotheses using a significance level of .10.

DATA:
```{r}
n <- 91
n_spoiled <- 16
p_0 <- 0.15
q_0 <- 1 - p_0
```

##According the HT procedure to design a hypothesis test for p ( complete 7 steps below)

1. $p =$ the true proportion of all commercial chardonnay bottles considered spoiled to some extent by cork-associated characteristics.

2. The null hypothesis is ?

**Answer:**
$H_{0}$ : p = 0.15


3. The alternative hypothesis is ?
**Answer:**
$H_{a}$ : p > 0.15

4. Since $np_0 = 91(.15) > 10$ and $nq_0 = 91(.85) = 77.35 > 10$, the large-sample $z$ test can be used. 
The test statistic value is

```{r}
# type the code here
# Given data
n <- 91
n_spoiled <- 16
p_0 <- 0.15
q_0 <- 1 - p_0

# Compute sample proportion
p_hat <- n_spoiled / n

# Compute standard error
SE <- sqrt(p_0 * q_0 / n)

# Compute z-score
z <- (p_hat - p_0) / SE
z
```


5. The form of $H_a$ implies that an upper-tailed test is appropriate: 

rejection region is?
```{r}
# type the code here
# Significance level
alpha <- 0.10

# Compute critical value
z_critical <- qnorm(1 - alpha)

# Display rejection region
z_critical
```

6. then $z$ test statistic value is ?
```{r}
# type the code here
# Given data
n <- 91
n_spoiled <- 16
p_0 <- 0.15
q_0 <- 1 - p_0

# Compute sample proportion
p_hat <- n_spoiled / n

# Compute standard error
SE <- sqrt(p_0 * q_0 / n)

# Compute z-score (test statistic)
z <- (p_hat - p_0) / SE
z
```

7. decision:

**Answer:**
If z>1.28, we reject $H_{0}$. 
If z <= 1.28, we fail to reject $H_{0}$

The computed value of z is 0.6899094. Hence, the decision is "we fail to reject $H_{0}$. Or in other words, we cannot accept the claim that more than 15% of the commercial chardonnay bottles are contaminated in this way at 10% significance level." 


