---
title: "Homwork3-Devore Ch10&11 "
author: "Homework03Gr6"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### NOTE: only those who contributes and fully participates in the work will get credit

**Scribe:**

**Moderator:**

**All contributors:**






**Attention:** 
If applicable, please finish all 8 problems step by step, rather than using the advance functions `aov`. However, you are encouraged to use more advance functions to check your solutions. For the problems that are difficult to implement by steps (eg. plot simultaneously CI) you can use advanced functions. 




##Q1 Devore 2nd edition 10.1.6
```{r D10.1.6}
#Data
carbonate <- c(20.5, 28.1, 27.8, 27.0, 28.0, 25.2, 25.3, 27.1, 20.5, 31.3)
silicate <- c(26.3, 24.0, 26.2, 20.2, 23.7, 34.0, 17.1, 26.8, 23.7, 24.9)
magnetite <- c(29.5, 34.0, 27.5, 29.4, 27.9, 26.2, 29.9, 29.5, 30.0, 35.6)
hematite <- c(36.5, 44.2, 34.1, 30.3, 31.4, 33.1, 34.1, 32.9, 36.3, 25.5)

total_fe <- c(carbonate, silicate, magnetite, hematite)
formation_type <- factor(rep(c("carbonate", "silicate", "magnetite", "hematite"), each = 10))
data <- data.frame(total_fe, formation_type)

mean_carbonate <- mean(carbonate)
mean_silicate <- mean(silicate)
mean_magnetite <- mean(magnetite)
mean_hematite <- mean(hematite)

grand_mean <- mean(total_fe)

#Sum of squares between groups
n_per_group <- length(carbonate) # 10 observations per group
ssb <- n_per_group * ((mean_carbonate - grand_mean)^2 + 
                       (mean_silicate - grand_mean)^2 + 
                       (mean_magnetite - grand_mean)^2 + 
                       (mean_hematite - grand_mean)^2)

#Sum of squares within group

ssw_carbonate <- sum((carbonate - mean_carbonate)^2)
ssw_silicate <- sum((silicate - mean_silicate)^2)
ssw_magnetite <- sum((magnetite - mean_magnetite)^2)
ssw_hematite <- sum((hematite - mean_hematite)^2)

ssw <- ssw_carbonate + ssw_silicate + ssw_magnetite + ssw_hematite

#Degree of Freedom

k <- 4 # Number of groups
n <- length(total_fe) # Total number of observations

dfb <- k - 1
dfw <- n - k

#Calculate Mean Squares Between (MSB) and Mean Squares Within (MSW)
msb <- ssb / dfb
msw <- ssw / dfw

#f value
f_value <- msb / msw

#p value
p_value <- pf(f_value, dfb, dfw, lower.tail = FALSE)

#ANOVA table
cat("ANOVA Table:\n")
cat("Source        df     SS       MS       F       P\n")
cat("Between       ", dfb, "  ", round(ssb, 2), "  ", round(msb, 2), "  ", round(f_value, 4), "  ", format(p_value, scientific = TRUE, digits = 3), "\n")
cat("Within        ", dfw, "  ", round(ssw, 2), "  ", round(msw, 2), "  ", "-\t\t -","\n")
cat("Total         ", n - 1, "  ", round(ssb + ssw, 2), "  ", "-\t\t -", "  ", "-\t\t -","\n")

alpha <- 0.01

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.01), so we reject the null hypothesis. There are significant differences in total Fe among the four types of iron formations.\n")
} else {
  cat("The p-value is greater than the significance level (0.01), so we fail to reject the null hypothesis. There is not enough evidence to conclude that there are significant differences in total Fe among the four types of iron formations.\n")
}
```
```{r 10.1.7}
#Given Information

#Number of mixtures (k) = 6
#Measurements per mixture (n_per_mixture) = 26
#Total observations (N) = 6 * 26 = 156
#SS (Mixture) = 5664.415
#MS (Error) = 13.929

#Degrees of Freedom (df)
#df (Mixture) = k - 1 = 6 - 1 = 5
#df (Total) = N - 1 = 156 - 1 = 155
#df (Error) = df (Total) - df (Mixture) = 155 - 5 = 150

#Sum of Squares (SS)
#MS (Mixture) = SS (Mixture) / df (Mixture)
#MS (Mixture) = 5664.415 / 5 = 1132.883
#SS (Error) = MS (Error) * df (Error)
#SS (Error) = 13.929 * 150 = 2089.35
#SS (Total) = SS (Mixture) + SS (Error)
#SS (Total) = 5664.415 + 2089.35 = 7753.765

#F-Statistic
#F = MS (Mixture) / MS (Error)
#F = 1132.883 / 13.929 = 81.332

#P value
df_mixture <- 5
df_error <- 150
f_value <- 81.332

p_value <- pf(f_value, df_mixture, df_error, lower.tail = FALSE)

cat("P-value:", p_value, "\n")

cat("ANOVA Table:\n")
cat("Source     df     SS        MS        F        P\n")
cat("Mixture    ", df_mixture, "    ", round(5664.415, 3), "    ", round(1132.883, 3), "    ", round(81.332, 3), "    ", format(p_value, scientific = TRUE, digits = 3), "\n")
cat("Error      ", df_error, "   ", round(2089.35, 3), "    ", round(13.929, 3), "    -        -\n")
cat("Total      ", 155, "   ", round(7753.765, 3), "    -        -        -\n")

alpha <- 0.01

if (p_value < alpha) {
  cat("The P-value is less than the significance level (0.01), so we reject the null hypothesis.\n")
  cat("There is compelling evidence that the true average electrical resistivity is not the same for all six mixtures.\n")
} else {
  cat("The P-value is greater than the significance level (0.01), so we fail to reject the null hypothesis.\n")
  cat("There is not enough evidence to conclude that the true average electrical resistivity is not the same for all six mixtures.\n")
}
```

```{r 10.1.8}
#Data
plate_4 <- c(309.2, 409.5, 311.0, 326.5, 316.8, 349.8, 309.7)
plate_6 <- c(402.1, 347.2, 361.0, 404.5, 331.0, 348.9, 381.7)
plate_8 <- c(392.4, 366.2, 351.0, 357.1, 409.9, 367.3, 382.0)
plate_10 <- c(346.7, 452.9, 461.4, 433.1, 410.6, 384.2, 362.6)
plate_12 <- c(407.4, 441.8, 419.9, 410.7, 473.4, 441.2, 465.8)

axial_stiffness <- c(plate_4, plate_6, plate_8, plate_10, plate_12)
plate_length <- factor(rep(c("4", "6", "8", "10", "12"), each = 7))
data <- data.frame(axial_stiffness, plate_length)

mean_4 <- mean(plate_4)
mean_6 <- mean(plate_6)
mean_8 <- mean(plate_8)
mean_10 <- mean(plate_10)
mean_12 <- mean(plate_12)

grand_mean <- mean(axial_stiffness)

n_per_group <- length(plate_4) # 7 observations per group
ssb <- n_per_group * ((mean_4 - grand_mean)^2 + 
                       (mean_6 - grand_mean)^2 + 
                       (mean_8 - grand_mean)^2 + 
                       (mean_10 - grand_mean)^2 + 
                       (mean_12 - grand_mean)^2)

ssw_4 <- sum((plate_4 - mean_4)^2)
ssw_6 <- sum((plate_6 - mean_6)^2)
ssw_8 <- sum((plate_8 - mean_8)^2)
ssw_10 <- sum((plate_10 - mean_10)^2)
ssw_12 <- sum((plate_12 - mean_12)^2)

ssw <- ssw_4 + ssw_6 + ssw_8 + ssw_10 + ssw_12

k <- 5 # Number of groups
n <- length(axial_stiffness) # Total number of observations

dfb <- k - 1
dfw <- n - k

msb <- ssb / dfb
msw <- ssw / dfw

f_value <- msb / msw

p_value <- pf(f_value, dfb, dfw, lower.tail = FALSE)

cat("ANOVA Table:\n")
cat("Source        df     SS       MS       F       P\n")
cat("Plate Length  ", dfb, "  ", round(ssb, 2), "  ", round(msb, 2), "  ", round(f_value, 4), "  ", format(p_value, scientific = TRUE, digits = 3), "\n")
cat("Error         ", dfw, "  ", round(ssw, 2), "  ", round(msw, 2), "  ", "-\t\t -","\n")
cat("Total         ", n - 1, "  ", round(ssb + ssw, 2), "  ", "-\t\t -", "  ", "-\t\t -","\n")

alpha <- 0.01

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.01), so we reject the null hypothesis.\n")
  cat("There is evidence that variation in plate length has an effect on true average axial stiffness.\n")
} else {
  cat("The p-value is greater than the significance level (0.01), so we fail to reject the null hypothesis.\n")
  cat("There is not enough evidence to conclude that variation in plate length has an effect on true average axial stiffness.\n")
}
```

```{r 10.2.18}
#Data
hormone_1 <- c(13, 17, 7, 14)
hormone_2 <- c(21, 13, 20, 17)
hormone_3 <- c(18, 15, 20, 17)
hormone_4 <- c(7, 11, 18, 10)
hormone_5 <- c(6, 11, 15, 8)

plant_growth <- c(hormone_1, hormone_2, hormone_3, hormone_4, hormone_5)
hormone_type <- factor(rep(c("1", "2", "3", "4", "5"), each = 4))
data <- data.frame(plant_growth, hormone_type)

mean_1 <- mean(hormone_1)
mean_2 <- mean(hormone_2)
mean_3 <- mean(hormone_3)
mean_4 <- mean(hormone_4)
mean_5 <- mean(hormone_5)

grand_mean <- mean(plant_growth)

n_per_group <- length(hormone_1) # 4 observations per group
ssb <- n_per_group * ((mean_1 - grand_mean)^2 + 
                       (mean_2 - grand_mean)^2 + 
                       (mean_3 - grand_mean)^2 + 
                       (mean_4 - grand_mean)^2 + 
                       (mean_5 - grand_mean)^2)

ssw_1 <- sum((hormone_1 - mean_1)^2)
ssw_2 <- sum((hormone_2 - mean_2)^2)
ssw_3 <- sum((hormone_3 - mean_3)^2)
ssw_4 <- sum((hormone_4 - mean_4)^2)
ssw_5 <- sum((hormone_5 - mean_5)^2)

ssw <- ssw_1 + ssw_2 + ssw_3 + ssw_4 + ssw_5

k <- 5 # Number of groups
n <- length(plant_growth) # Total number of observations

dfb <- k - 1
dfw <- n - k


msb <- ssb / dfb
msw <- ssw / dfw

f_value <- msb / msw

p_value <- pf(f_value, dfb, dfw, lower.tail = FALSE)

cat("ANOVA Table:\n")
cat("Source        df     SS       MS       F       P\n")
cat("Hormone Type  ", dfb, "  ", round(ssb, 2), "  ", round(msb, 2), "  ", round(f_value, 4), "  ", format(p_value, scientific = TRUE, digits = 3), "\n")
cat("Error         ", dfw, "  ", round(ssw, 2), "  ", round(msw, 2), "  ", "-\t\t -","\n")
cat("Total         ", n - 1, "  ", round(ssb + ssw, 2), "  ", "-\t\t -", "  ", "-\t\t -","\n")


alpha <- 0.05

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis.\n")
  cat("There is evidence that different hormone types affect plant growth.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis.\n")
  cat("There is not enough evidence to conclude that different hormone types affect plant growth.\n")
}

q_value <- qtukey(0.95, k, dfw) # Get the studentized range statistic
msw_value <- msw
n_per_group <- length(hormone_1)
hsd <- q_value * sqrt(msw_value / n_per_group)

cat("Tukey's HSD:", hsd, "\n")


means <- c(mean_1, mean_2, mean_3, mean_4, mean_5)
hormone_names <- c("1", "2", "3", "4", "5")

cat("Pairwise Comparisons:\n")
for (i in 1:(k - 1)) {
  for (j in (i + 1):k) {
    diff <- abs(means[i] - means[j])
    if (diff > hsd) {
      cat("Hormone", hormone_names[i], "vs Hormone", hormone_names[j], ": Significant difference (", diff, " > ", hsd, ")\n")
    } else {
      cat("Hormone", hormone_names[i], "vs Hormone", hormone_names[j], ": No significant difference (", diff, " <= ", hsd, ")\n")
    }
  }
}


```

```{r 10.3.27}

#Data
brand_1 <- c(7.9, 6.2, 6.6, 8.6, 8.9, 10.1, 9.6)
brand_2 <- c(5.7, 7.5, 9.8, 6.1, 8.4)
brand_3 <- c(6.8, 7.5, 5.0, 7.4, 5.3, 6.1)
brand_4 <- c(6.4, 7.1, 7.9, 4.5, 5.0, 4.0)

folacin_content <- c(brand_1, brand_2, brand_3, brand_4)
brand <- factor(rep(c("1", "2", "3", "4"), c(length(brand_1), length(brand_2), length(brand_3), length(brand_4))))
data <- data.frame(folacin_content, brand)

anova_result <- aov(folacin_content ~ brand, data = data)
summary(anova_result)

alpha <- 0.05
summary_table <- summary(anova_result)
f_value <- summary_table[[1]]$`F value`[1]
p_value <- summary_table[[1]]$`Pr(>F)`[1]

cat("F-value:", f_value, "\n")
cat("P-value:", p_value, "\n")

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis. There are significant differences in folacin content among the brands.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis. There is not enough evidence to conclude that there are significant differences in folacin content among the brands.\n")
}

##Assess assumptions

# Normality of Residuals
qqnorm(residuals(anova_result))
qqline(residuals(anova_result))

# Homogeneity of Variances (Levene's Test)
library(car)
leveneTest(folacin_content ~ brand, data = data)

# Boxplots for visual inspection
boxplot(folacin_content ~ brand, data = data, main = "Folacin Content by Brand")

tukey_result <- TukeyHSD(anova_result)
print(tukey_result)

cat("Tukey's HSD Test Results:\n")
print(tukey_result)

cat("\nInterpretation:\n")
for (i in 1:nrow(tukey_result$brand)) {
  if (tukey_result$brand[i, 4] < 0.05) {
    cat(rownames(tukey_result$brand)[i], "shows a significant difference.\n")
  } else {
    cat(rownames(tukey_result$brand)[i], "shows no significant difference.\n")
  }
}


```

```{r 11.1.4}
paint_data <- matrix(c(54, 46, 51, 46, 44, 47, 39, 42, 44, 44, 37, 43), nrow = 4, byrow = TRUE)
rownames(paint_data) <- c("Paint 1", "Paint 2", "Paint 3", "Paint 4")
colnames(paint_data) <- c("Roller 1", "Roller 2", "Roller 3")

#a. ANNOVA table
# Calculate totals
paint_totals <- rowSums(paint_data)
roller_totals <- colSums(paint_data)
grand_total <- sum(paint_data)

# Calculate means
paint_means <- paint_totals / ncol(paint_data)
roller_means <- roller_totals / nrow(paint_data)
grand_mean <- grand_total / (nrow(paint_data) * ncol(paint_data))

# Calculate sums of squares
ss_paint <- ncol(paint_data) * sum((paint_means - grand_mean)^2)
ss_roller <- nrow(paint_data) * sum((roller_means - grand_mean)^2)
ss_total <- sum((paint_data - grand_mean)^2)
ss_error <- ss_total - ss_paint - ss_roller

# Calculate degrees of freedom
df_paint <- nrow(paint_data) - 1
df_roller <- ncol(paint_data) - 1
df_error <- (nrow(paint_data) - 1) * (ncol(paint_data) - 1)
df_total <- nrow(paint_data) * ncol(paint_data) - 1

# Calculate mean squares
ms_paint <- ss_paint / df_paint
ms_roller <- ss_roller / df_roller
ms_error <- ss_error / df_error

# Calculate F-statistics
f_paint <- ms_paint / ms_error
f_roller <- ms_roller / ms_error

# Create ANOVA table
anova_table <- data.frame(
  Source = c("Paint Brand", "Roller Brand", "Error", "Total"),
  df = c(df_paint, df_roller, df_error, df_total),
  SS = c(ss_paint, ss_roller, ss_error, ss_total),
  MS = c(ms_paint, ms_roller, ms_error, NA),
  F = c(f_paint, f_roller, NA, NA)
)

print(anova_table)

#b) Test Hypotheses for Paint Brand
alpha <- 0.05
p_value_paint <- pf(f_paint, df_paint, df_error, lower.tail = FALSE)

cat("Paint Brand Test:\n")
cat("F-statistic:", f_paint, "\n")
cat("P-value:", p_value_paint, "\n")

if (p_value_paint < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis.\n")
  cat("There is evidence that paint brand has an effect on coverage.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis.\n")
  cat("There is not enough evidence to conclude that paint brand has an effect on coverage.\n")
}

#c) Test Hypotheses for Roller Brand
p_value_roller <- pf(f_roller, df_roller, df_error, lower.tail = FALSE)

cat("\nRoller Brand Test:\n")
cat("F-statistic:", f_roller, "\n")
cat("P-value:", p_value_roller, "\n")

if (p_value_roller < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis.\n")
  cat("There is evidence that roller brand has an effect on coverage.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis.\n")
  cat("There is not enough evidence to conclude that roller brand has an effect on coverage.\n")
}

#d) Tukey's Method
q_value <- qtukey(0.95, nrow(paint_data), df_error)
hsd <- q_value * sqrt(ms_error / ncol(paint_data))

cat("\nTukey's HSD:", hsd, "\n")

# Pairwise comparisons
paint_means_original <- paint_means + 400
paint_names <- rownames(paint_data)

cat("\nPairwise Comparisons (Original Scale):\n")
for (i in 1:(nrow(paint_data) - 1)) {
  for (j in (i + 1):nrow(paint_data)) {
    diff <- abs(paint_means_original[i] - paint_means_original[j])
    if (diff > hsd) {
      cat(paint_names[i], "vs", paint_names[j], ": Significant difference (", diff, " > ", hsd, ")\n")
    } else {
      cat(paint_names[i], "vs", paint_names[j], ": No significant difference (", diff, " <= ", hsd, ")\n")
    }
  }
}

```

```{r 11.1.10}
#Data
method_A <- c(30.7, 29.1, 30.0, 31.9, 30.5, 26.9, 28.2, 32.4, 26.6, 28.6)
method_B <- c(33.7, 30.6, 32.2, 34.6, 33.0, 29.3, 28.4, 32.4, 29.5, 29.4)
method_C <- c(30.5, 32.6, 30.5, 33.5, 32.4, 27.8, 30.7, 33.6, 29.2, 33.2)

compressive_strength <- c(method_A, method_B, method_C)
curing_method <- factor(rep(c("A", "B", "C"), each = 10))
data <- data.frame(compressive_strength, curing_method)

anova_result <- aov(compressive_strength ~ curing_method, data = data)
summary(anova_result)

alpha <- 0.05
summary_table <- summary(anova_result)
f_value <- summary_table[[1]]$`F value`[1]
p_value <- summary_table[[1]]$`Pr(>F)`[1]

cat("F-value:", f_value, "\n")
cat("P-value:", p_value, "\n")

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis. There are significant differences in compressive strength among the three curing methods.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis. There is not enough evidence to conclude that there are significant differences in compressive strength among the three curing methods.\n")
}

#Assess assumptions by Anova

alpha <- 0.05
summary_table <- summary(anova_result)
f_value <- summary_table[[1]]$`F value`[1]
p_value <- summary_table[[1]]$`Pr(>F)`[1]

cat("F-value:", f_value, "\n")
cat("P-value:", p_value, "\n")

if (p_value < alpha) {
  cat("The p-value is less than the significance level (0.05), so we reject the null hypothesis. There are significant differences in compressive strength among the three curing methods.\n")
} else {
  cat("The p-value is greater than the significance level (0.05), so we fail to reject the null hypothesis. There is not enough evidence to conclude that there are significant differences in compressive strength among the three curing methods.\n")
}


# Normality of Residuals
qqnorm(residuals(anova_result))
qqline(residuals(anova_result))

# Homogeneity of Variances (Levene's Test)
library(car)
leveneTest(compressive_strength ~ curing_method, data = data)

# Boxplots for visual inspection
boxplot(compressive_strength ~ curing_method, data = data, main = "Compressive Strength by Curing Method")
#Multiple comparsison results
tukey_result <- TukeyHSD(anova_result)
print(tukey_result)

cat("Tukey's HSD Test Results:\n")
print(tukey_result)

cat("\nInterpretation:\n")
for (i in 1:nrow(tukey_result$curing_method)) {
  if (tukey_result$curing_method[i, 4] < 0.05) {
    cat(rownames(tukey_result$curing_method)[i], "shows a significant difference.\n")
  } else {
    cat(rownames(tukey_result$curing_method)[i], "shows no significant difference.\n")
  }
}

```

```{r 11.2.16}
#given data

#Factor A: Curing Time (3 levels)
#Factor B: Type of Mix (4 levels)
#Observations per combination: 3
SSA <- 30763.0
SSB <- 34185.6
SSE <- 97436.8
SST <- 205966.6
#x̄₁.. = 4010.88, x̄₂.. = 4029.10, x̄₃.. = 3960.

#Degrees of Freedom (df)

#dfA = a - 1 = 3 - 1 = 2
#dfB = b - 1 = 4 - 1 = 3
#dfAB = dfA * dfB = 2 * 3 = 6
#dfE = N - ab = 36 - 12 = 24
#dfT = N - 1 = 36 - 1 = 35
#Sum of Squares Interaction (SSAB)
#SSAB = SST - SSA - SSB - SSE
#SSAB = 205,966.6 - 30,763.0 - 34,185.6 - 97,436.8
SSAB <- 43581.2

#Mean Squares (MS)
#MSA = SSA / dfA 
MSA <- 15381.5
#MSB = SSB / dfB
MSB <- 11395.2
#MSAB = SSAB / dfAB
MSAB <- 7263.53
#MSE = SSE / dfE 
MSE <- 4059.87

#F-Statistics

#FA = MSA / MSE 
FA <-  3.79
#FB = MSB / MSE 
FB <-  2.81
#FAB = MSAB / MSE 
FAB <- 1.79

dfA <- 2
dfB <- 3
dfAB <- 6
dfT <- 35
dfE <- 24
FA <- 3.79
FB <- 2.81
FAB <- 1.79

p_value_A <- pf(FA, dfA, dfE, lower.tail = FALSE)
p_value_B <- pf(FB, dfB, dfE, lower.tail = FALSE)
p_value_AB <- pf(FAB, dfAB, dfE, lower.tail = FALSE)

cat("P-value for Factor A:", p_value_A, "\n")
cat("P-value for Factor B:", p_value_B, "\n")
cat("P-value for Interaction:", p_value_AB, "\n")

#a. ANNOVA TABLE

anova_table <- data.frame(
  Source = c("Curing Time (A)", "Type of Mix (B)", "Interaction (AB)", "Error", "Total"),
  df = c(dfA, dfB, dfAB, dfE, dfT),
  SS = c(SSA, SSB, SSAB, SSE, SST),
  MS = c(MSA, MSB, MSAB, MSE, NA),
  F = c(FA, FB, FAB, NA, NA),
  P = c(p_value_A, p_value_B, p_value_AB, NA, NA)
)

print(anova_table)

#b. Test interaction (AB)

alpha <- 0.05
if (p_value_AB < alpha) {
  cat("The p-value for interaction is less than 0.05. Reject H0AB. There is a significant interaction.\n")
} else {
  cat("The p-value for interaction is greater than 0.05. Fail to reject H0AB. There is no significant interaction.\n")
}

#c. Test factor A (curing time)
if (p_value_A < alpha) {
  cat("The p-value for Factor A is less than 0.05. Reject H0A. There is a significant effect of curing time.\n")
} else {
  cat("The p-value for Factor A is greater than 0.05. Fail to reject H0A. There is no significant effect of curing time.\n")
}

#d. Test Factor B (Type of Mix)
if (p_value_B < alpha) {
  cat("The p-value for Factor B is less than 0.05. Reject H0B. There is a significant effect of type of mix.\n")
} else {
  cat("The p-value for Factor B is greater than 0.05. Fail to reject H0B. There is no significant effect of type of mix.\n")
}

#e. Tukey's Procedure for Curing Times

means <- c(4010.88, 4029.10, 3960.02)
names <- c("Curing Time 1", "Curing Time 2", "Curing Time 3")
k <- 3
n <- 4 * 3 # observations per curing time

q_value <- qtukey(0.95, k, dfE)
hsd <- q_value * sqrt(MSE / n)

cat("Tukey's HSD:", hsd, "\n")

# Pairwise comparisons
cat("\nPairwise Comparisons:\n")
for (i in 1:(k - 1)) {
  for (j in (i + 1):k) {
    diff <- abs(means[i] - means[j])
    if (diff > hsd) {
      cat(names[i], "vs", names[j], ": Significant difference (", diff, " > ", hsd, ")\n")
    } else {
      cat(names[i], "vs", names[j], ": No significant difference (", diff, " <= ", hsd, ")\n")
    }
  }
}
```

