---
title: "Homwork2-Exam 1 Preparation HW "
author: "Homework02Gr#" #change to your group number
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### NOTE: only those who contributes and fully participates in the work will get credit

**Scribe:**

**Moderator:**

**All contributors:**



This homework is accumulative, with the intention of assisting you to prepare for Exam1. 
It is due Wednesday 11:59pm, you will get extra 10pts for this HW if you finish it by Tuesday 11:59pm. Yes, I know it has lots of problems,  but I believe that you want to perform well for the coming exam, so this HW will be very beneficial!



**Attention:** 
Please finish all 14 problems step by step, rather than using the advance functions `t.test`, `prop.test`. However, you are encouraged to use more advance functions to check your solutions. 




##Q1 Devore 2nd edition 7.1.5
Assume that the helium porosity (in percentage) of coal sam- ples taken from any particular seam is normally distributed with true standard deviation .75.
a. Compute a 95% CI for the true average porosity of a cer-
tain seam if the average porosity for 20 specimens from
the seam was 4.85.
```{r D7.1.5 a}
alpha = 0.05
n = 20
sd = .75
xbar = 4.85

z_alpha = 1.96

CL_Lower = xbar - z_alpha*(sd/sqrt(n));CL_Lower
CL_Upper = xbar + z_alpha*(sd/sqrt(n));CL_Upper
```

b. Compute a 98% CI for true average porosity of another
seam based on 16 specimens with a sample average poros-
ity of 4.56.
```{r D7.1.5 b}

n = 16
sd = .75
xbar = 4.56

z_alpha = 2.326

CL_Lower = xbar - z_alpha*(sd/sqrt(n));CL_Lower
CL_Upper = xbar + z_alpha*(sd/sqrt(n));CL_Upper
```
c. How large a sample size is necessary if the width of the
95% interval is to be .40?
```{r D7.1.5 c}
z_alpha = 1.96
sd = .75
w = .40
#width is margin of error times 2
n = (2*(z_alpha)*(sd/w))^2;ceiling(n)


```
d. What sample size is necessary to estimate true average
porosity to within .2 with 99% confidence?
```{r D7.1.5 d}
z_alpha = 2.576
sd = .75
E = .2
#within means marigin of error
n = ((z_alpha)*(sd/w))^2;ceiling(n)


```


##Q2 Devore 2nd edition 7.2.13
The article “Gas Cooking, Kitchen Ventilation, and Exposure to Combustion Products” (Indoor Air, 2006: 65–73) reported that for a sample of 50 kitchens with gas cooking appliances monitored during a one-week period,
the sample mean CO2 level (ppm) was 654.16, and the sam- ple standard deviation was 164.43.
a. Calculate and interpret a 95% (two-sided) confidence
interval for true average CO2 level in the population of
all homes from which the sample was selected.
b. Suppose the investigators had made a rough guess of 175 for the value of s before collecting data. What sample size would be necessary to obtain an interval width of 50
ppm for a confidence level of 95%?
```{r D7.2.13 a}
n = 50
xbar = 654.16
s = 164.43
alpha = 1 - .95
#Two sided so alpha is divided by 2
z_alpha = qnorm(alpha/2, lower.tail = FALSE);z_alpha

CL_Lower = xbar - z_alpha*(s/sqrt(n));CL_Lower
CL_Upper = xbar + z_alpha*(s/sqrt(n));CL_Upper
```

```{r D7.2.13 b}
w = 50
xbar = 654.16
s = 175
alpha = 1 - .95
#Two sided so alpha is divided by 2
z_alpha = qnorm(alpha/2, lower.tail = FALSE);z_alpha

n = (2*(z_alpha)*(s/w))^2;ceiling(n)
```
##Q3 Devore 2nd edition 7.2.20
The Associated Press (October 9, 2002) reported that in a survey of 4722 American youngsters aged 6 to 19, 15% were seriously overweight (a body mass index of at least 30; this index is a measure of weight relative to height). Calculate and interpret a confidence interval using a 99% confidence level for the proportion of all American young- sters who are seriously overweight.
```{r D7.2.20}
n = 4722
#Huge sample so we can approximate 
pbar = .15
qbar = 1 - pbar
alpha = 1 - .99
z_alpha = qnorm(alpha/2, lower.tail = FALSE);z_alpha

CL_Lower = pbar - z_alpha*sqrt((qbar*pbar)/n);CL_Lower
CL_Upper = pbar + z_alpha*sqrt((qbar*pbar)/n);CL_Upper


```
##Q4 Devore 2nd edition 7.3.36
The n = 26 observations on escape time given in Exercise 36 of Chapter 1 give a sample mean and sample standard deviation of 370.69 and 24.36, respectively.
a. Calculate an upper confidence bound for population
mean escape time using a confidence level of 95%.
b. Calculate an upper prediction bound for the escape time of a single additional worker using a prediction level of 95%. How does this bound compare with the confidence
bound of part (a)?
c. Suppose that two additional workers will be chosen to
participate in the simulated escape exercise. Denote their escape times by X27 and X28, and let Xnew denote the aver- age of these two values. Modify the formula for a PI for a single x value to obtain a PI for Xnew, and calculate a 95% two-sided interval based on the given escape data.

```{r 7.3.36 a}
n = 26
xbar = 370.69
sd = 24.36

#Cant use CLT so must use T distrobution

alpha = 1 - .95
#We care about the upper tail
T_alpha = qt(alpha,n - 1, lower.tail = FALSE);T_alpha
CI_Upper = xbar + T_alpha*(sd/sqrt(n));CI_Upper
```

```{r 7.3.36 b}
n = 26
xbar = 370.69
sd = 24.36

#Cant use CLT so must use T distrobution

alpha = 1 - .95
#We care about the upper tail
T_alpha = qt(alpha,n - 1, lower.tail = FALSE);T_alpha
SE = sd*sqrt(1+(1/n))
PI_Upper = xbar + T_alpha*SE;PI_Upper
#This bound is higher than the CI in part a. The probability would be lower as the area is smaller.
```
```{r 7.3.36 c}
#Not sure what to do here....
```

##Q5 Devore 2nd edition 8.1.13
Let X1,..., Xn denote a random sample from a normal population distribution with a known value of s.
a. For testing the hypotheses H0: m = m0 versus Ha: m > m0 (where m0 is a fixed number), show that the
test with test statistic X and rejection region
x >= m0 + 2.33*s/sqrt(n) has significance level .01.

b. Suppose the procedure of part (a) is used to test H0:m <= m0 versus Ha:m > m0. If m0 = 100,n = 25, and s = 5, what is the probability of committing a type I error when m = 99? When m = 98? In general, what can be said about the probability of a type I error when the actual value of m is less than m ?  In general, what can be said about the probability of a type I error when the actual value of m is less than m0 ?Verify your assertion.
```{r 8.1.13 a}
#Because it is a normal random value and known sigma we can use the z distrobution.
#Lets say alpha is 0.01
alpha = 0.01
z_alpha =qnorm(0.01,lower.tail = FALSE);z_alpha
#also
alpha = 1 - pnorm(2.33);alpha
#If we pick any m0 or n that would would work under CLT, we can prove that x would be at least equal or more than z_alpha. Therefore this test has a significance of .01
```
```{r 8.1.13 b}
#H0:m <= m0
#Ha:m > m0
mu0 = 100
n = 25
s = 5
#They state it is normal.
#if mu is 99
mu = 99
xbar = mu0 + 2.33*(s/sqrt(n))
z_test = (xbar - mu)/(s/sqrt(n))
#Type 1 error:
probability = 1 - pnorm(z_test);probability
#Type 1 error with mu = 98
mu = 98
z_test = (xbar - mu)/(s/sqrt(n))
probability = 1 - pnorm(z_test);probability

#The probability of a Type I error decreases as the actual value of mu becomes less than mu0.
```
##Q6 Devore 2nd edition 8.2.21
The true average diameter of ball bearings of a certain type is supposed to be .5 in. A one-sample t test will be carried out to see whether this is the case. What conclusion is appropriate in each of the following situations?
a. n=13,t=1.6,alpha=.05
b. n=13,t=21.6,alpha=.05
c. n=25,t=22.6,alpha=.01 
d. n=25,t=23.9

```{r 8.2.21}
xbar = 0.5
#H0 = 0.5
#part a
n = 13
t = 1.6
alpha = .05

t_test = qt((1-alpha/2),n-1);t_test
#This is greater than t so we fail to reject H0

#part b
n = 13
t = 21.6
alpha = .05

t_test = qt((1-alpha/2),n-1);t_test
#This is less than t so we reject H0

#part c
n = 25
t = 22.6
alpha = .01

t_test = qt((1-alpha/2),n-1);t_test
#This is less than t so we reject H0

#part d
n = 25
t = 23.9
alpha = .05

t_test = qt((1-alpha/2),n-1);t_test
#This is less than t so we reject H0
#Because this occurs for .05 and t is so large. This is happen for each alpha. 

```
##Q7 Devore 2nd edition 8.3.34
doesn't exist??

##More Problems here 
continue to solve the following problems in  the format of the layout of Q1.

Devore BOOK : 
7.2.13 
7.2.20
7.3.36
8.1.13
8.2.21
8.3.34
8.4.48
9.1.6
9.2.24
9.3.40
9.4.50
9.5.63
9.5.66
